Covid-19 A Spatio-Temporal Investigation.

### 2021-01-03 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the Spatio-temporal aspects of the Covid-19 pandemic should be conducted, by evaluating the number of cases and deaths in different countries accordingly to time in the year of 2020 we can contribute with methods to analyze Spatio-temporal behavior in future disease outbreaks.

>>>>

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the Spatio-temporal aspects of the Covid-19 pandemic should be conducted, by evaluating the number of cases and deaths in different countries accordingly to time in the year 2020 we can contribute with methods to analyze Spatio-temporal behavior in future disease outbreaks.
